### 2017-11-28 paper/sections/1_introduction.tex
paper: more typos and final read through
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Storage systems use software-based caches to improve performance but the
policies that guide what data to evict and when to evict vary with the use
case. For example, caching file system metadata on clients and servers reduces
the number of remote procedure calls and improves the performance of
create-heavy workloads common in HPC~\cite{ren:sc2014-indexfs,
patil:fast2011-giga+}. But the policies for what data to evict and when to
evict are specific to the application's behavior and the system's configuration
(hardware, settings, etc.) so a new workload may prove to be a poor match for
the selected caching
policy~\cite{xiao:socc15-shardfs,brandt:msst2003-lh,sevilla:sc15-mantle,
weil:sc2004-dyn-metadata, weil:osdi2006-ceph}. We evaluate a
variety of caching policies using our data management language/policy engine and
arrive at a customized policy that works well for our target application.  This
process of trying general policies and quickly iterating to a customized
solution shows that our prototype can be adapted to different workloads.

Our example application, ParSplice~\cite{perez:jctc20150parsplice}, is
representative of an important class of applications with similar working set
behaviors that extensively use software-based caches.  ParSplice is a molecular
dynamics simulation that uses a hierarchy of caches and a single persistent
key-value store to store both observed minima across a molecule's equation of
motion (EOM) and the hundreds or thousands of partial trajectories calculated
each second during a parallel job.  This workload is pervasive across
simulations that rely on a mesh-based decomposition of a physical region and
result in millions or billions of mesh cells, where each cell contains
materials, pressures, temperatures and other characteristics that are required
to accurately simulate phenomena of interest.  The fine-grained data annotation
capabilities provided by key-value storage is a natural match for these types
of scientific simulations.  Unfortunately, simulations of this size saturate
the capacity and bandwidth capabilities of a single node so we need more
effective data management techniques.

>>>>

Storage systems use software-based caches to improve performance but the
policies that guide what data to evict and when to evict vary with the use
case. For example, caching file system metadata on clients and servers reduces
the number of remote procedure calls and improves the performance of
create-heavy workloads common in HPC~\cite{ren:sc2014-indexfs,
patil:fast2011-giga+, weil:sc2004-dyn-metadata}. But the policies for what data
to evict and when to evict are specific to the application's behavior and the
hardware configuration so a new workload may prove to be a poor match for the
selected caching
policy~\cite{xiao:socc15-shardfs,brandt:msst2003-lh,sevilla:sc15-mantle,
weil:sc2004-dyn-metadata, weil:osdi2006-ceph}. We evaluate a variety of caching
policies using our data management language/policy engine and arrive at a
customized policy that works well for our example application,
ParSplice~\cite{perez:jctc20150parsplice}.

ParSplice, the molecular dynamics simulation, is representative of an important
class of HPC applications with similar working set behaviors that extensively
use software-based caches. It uses a hierarchy of caches and a single
persistent key-value store to store both observed minima across a molecule's
equation of motion (EOM) and the hundreds or thousands of partial trajectories
calculated each second during a parallel job.  This workload is pervasive
across simulations that (1) rely on a mesh-based decomposition of a physical
region and (2) result in millions or billions of mesh cells, where each cell
contains materials, pressures, temperatures and other characteristics that are
required to accurately simulate phenomena of interest.  The fine-grained data
annotation capabilities provided by key-value storage is a natural match for
these types of scientific simulations.  Unfortunately, simulations of this size
saturate the capacity and bandwidth capabilities of a single node so we need
more effective data management techniques.

### 2017-11-28 paper/sections/2_parsplice-keyspace-analysis.tex
paper: more typos and final read through
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

%\subsubsection*{Discussion}
%Why don't we just an LRU cache:
%\begin{itemize}
%  \item we can do better (workload is structured and has locality)
%  \item finding the size of the cache is hard
%  \item hotspots dissipate too quickly
%\end{itemize}

@@

All experiments ran on Trinitite, a Cray XC40 with 32 Intel Haswell 2.3GHz
cores per node.  Each node has 128GB of RAM and our goal is to limit the size
of the cache to 3\% of RAM . Note that this is an addition to the 30GB that
ParSplice uses to manage other ranks on the same node.  The scalability
experiment uses 1 splicer, 1 persistent database, 1 cache process, and up to 2
workers. We scale up to 1024 tasks, which spans 32 nodes and disable
hyper-threading because we experience unacceptable variability in performance.
For the rest of the experiments, we use 8 nodes, 1 splicer, 1 persistent
database, 1 cache process, 1 worker, and up to 256 tasks.  The keyspace
analysis that follows is for the cache on the worker node, which is circled in
Figure~\ref{fig:parsplice}.

@@

\begin{figure}[t]
  \noindent\includegraphics[width=0.5\textwidth]{figures/motivation-regimes.png}\\
  \caption{Key activity for ParSplice starts with many reads to a small set of
keys and progresses to less reads to a larger set of keys.  The line shows the
rate that EOM minima values are retrieved from the key-value store (\(y1\)
axis) and the points along the bottom show the number of keys accessed in a 1
second sliding window (\(y2\) axis). Despite having different growth rates
(\(\Delta\)), the structure and behavior of the key activities are similar.
\label{fig:motivation-regimes}}
\end{figure}

\begin{figure}[t]
  \noindent\includegraphics[width=0.5\textwidth]{figures/methodology-keys.png}\\
  \caption{ Over time, tasks start to access a larger set of keys resulting in
some keys being more popular than others.  Despite different growth rates
(\(\Delta\)), the spatial locality of key accesses is similar between the two
runs.  ({\it e.g.}, some keys are still read 5 times as many times others).
\label{fig:methodology-keys}}
\end{figure}

Our analysis shows that ParSplice accesses keys in a structured and predictable
way. The following 3 observations shape the policies we design later in the
paper.

@@

Figure~\ref{fig:motivation-regimes} shows how ParSplice tasks read key-value
pairs from the worker's cache for two different initial conditions of
\(\Delta\), which is the rate that new atoms enter the simulation.  The line is
the read request rate (\(y1\) axis) and the dots along the bottom are the
number of unique keys accessed (\(y2\) axis).  The \(\Delta_1\) growth rate
adds atoms every 100K microseconds while the \(\Delta_2\) growth rate adds
atoms every 1 million microseconds. So \(\Delta_2\) has a smaller growth rate
resulting in hotter keys and a smaller keyspace.  Values smaller than
\(\Delta_2\)'s growth rate or a temperature of 400 degrees results in very
little database activity because state transitions take too long. Similarly,
values larger than \(\Delta_1\)'s growth rate or a temperature of 4000 degrees
result in an equally meaningless simulation as transitions are unrealistic.
This figure demonstrates that small changes to \(\Delta\) can have a strong
effect on the timing and frequency with which new EOM minima are discovered and
referenced. This finding suggests that we need a flexible policy language and
engine to explore these trade-offs.

The bars in Figure~\ref{fig:methodology-keyspace} show \(50-100\times\) as many
reads (\texttt{get()}) as writes (\texttt{put()}).  Tasks read the same
key for extended periods because the trajectory gets stuck in so-called
superbasins composed of tightly connected sets of states. In this case, many
trajectory segments with the same coordinates are needed before the trajectory
moves on.  Writes only occur for the final state of segments generated by
tasks; their magnitude is smaller than reads because the caches ignore
redundant write requests. The number of read and write requests are highest at
the beginning of the run when tasks generate segments for the same state, which
is computationally cheap (this motivates Section~\S\ref{sec:arch-specific}).

\subsubsection{\underline{Entropy increases over time}} The reads per second in
Figure~\ref{fig:motivation-regimes} show that the number of requests decreases
and the number of active keys increases over time. The resulting key access
imbalance for the two growth rates in Figure~\ref{fig:motivation-regimes} are
shown in Figure~\ref{fig:methodology-keys}, where reads are plotted for each
unique state, or key, along the \(x\) axis. Keys are more popular than others
(up to \(5\times\)) because worker tasks start generating states with different
coordinates later in the run.  Figure~\ref{fig:methodology-keys} shows that the
number of reads changes with different initial conditions (\(\Delta\)), but
that the spatial locality of key accesses is similar ({\it e.g.}, some keys are
still \(5\times\) more popular than others).
Figure~\ref{fig:motivation-regimes} shows how entropy for different growth
rates has temporal locality, as the reads per second for \(\Delta_2\) look like
the reads per second for \(\Delta_1\) stretched out along the time axis.
Trends also exist for temperature and number of workers but are omitted here
for space. This structure means that we can learn the key access patterns and
adapt the storage system accordingly (this motivates
Section~\S\ref{sec:dom-specific}).

>>>>

@@

All experiments ran on Trinitite, a Cray XC40 with 32 Intel Haswell 2.3GHz
cores per node.  Each node has 128GB of RAM and our goal is to limit the size
of the cache to 3\% of RAM. Note that this is an addition to the 30GB that
ParSplice uses to manage other ranks on the same node.  The scalability
experiment uses 1 splicer, 1 persistent database, 1 cache process, and up to 2
workers. We scale up to 1024 tasks, which spans 32 nodes and disable
hyper-threading because we experience unacceptable variability in performance.
For the rest of the experiments, we use 8 nodes, 1 splicer, 1 persistent
database, 1 cache process, 1 worker, and up to 256 tasks.  The keyspace
analysis that follows is for the cache on the worker node, which is circled in
Figure~\ref{fig:parsplice}.

@@

Our analysis shows that ParSplice accesses keys in a structured and predictable
way. The following 4 observations shape the policies we design later in the
paper.

@@

The bars in Figure~\ref{fig:methodology-keyspace} show \(50-100\times\) as many
reads (\texttt{get()}) as writes (\texttt{put()}).  Tasks read the same key for
extended periods because the trajectory gets stuck in so-called superbasins
composed of tightly connected sets of states.  Writes only occur for the final
state of segments generated by tasks; their magnitude is smaller than reads
because the caches ignore redundant write requests.

\begin{figure}[t]
  \noindent\includegraphics[width=0.5\textwidth]{figures/motivation-regimes.png}\\
  \caption{Key activity for ParSplice starts with many reads to a small set of
keys and progresses to less reads to a larger set of keys.  The line shows the
rate that EOM minima values are retrieved from the key-value store (\(y1\)
axis) and the points along the bottom show the number of unique keys accessed in a 1
second sliding window (\(y2\) axis). Despite having different growth rates
(\(\Delta\)), the structure and behavior of the key activities are similar.
\label{fig:motivation-regimes}}
\end{figure}

\subsubsection{\underline{Initial conditions influence key activity}}
Figure~\ref{fig:motivation-regimes} shows how ParSplice tasks read key-value
pairs from the worker's cache for two different initial conditions of
\(\Delta\), which is the rate that new atoms enter the simulation.  The line is
the read request rate (\(y1\) axis) and the dots along the bottom are the
number of unique keys accessed (\(y2\) axis).  The \(\Delta_1\) growth rate
adds atoms every 100K microseconds while the \(\Delta_2\) growth rate adds
atoms every 1 million microseconds. So \(\Delta_2\) has a smaller growth rate
resulting in hotter keys and a smaller keyspace.  Values smaller than
\(\Delta_2\)'s growth rate or a temperature of 400 degrees result in very
little database activity because state transitions take too long. Similarly,
values larger than \(\Delta_1\)'s growth rate or a temperature of 4000 degrees
result in an equally meaningless simulation as transitions are unrealistic.
This figure demonstrates that small changes to \(\Delta\) can have a strong
effect on the timing and frequency with which new EOM minima are discovered and
referenced. This finding suggests that we need a flexible policy language and
engine to explore these trade-offs.

\begin{figure}[t]
  \noindent\includegraphics[width=0.5\textwidth]{figures/methodology-keys.png}\\
  \caption{Over time, tasks start to access a larger set of keys resulting in
some keys being more popular than others.  Despite different growth rates
(\(\Delta\)), the spatial locality of key accesses is similar between the two
runs.  ({\it e.g.}, some keys are still read 5 times as many times others).
\label{fig:methodology-keys}}
\end{figure}

\subsubsection{\underline{Entropy increases over time}} The reads per second in
Figure~\ref{fig:motivation-regimes} show that the number of requests decreases
and the number of active keys increases over time.  The number of read and
write requests are highest at the beginning of the run when tasks generate
segments for the same state, which is computationally cheap (this motivates
Section~\S\ref{sec:arch-specific}).  The resulting key access imbalance for the
two growth rates in Figure~\ref{fig:motivation-regimes} are shown in
Figure~\ref{fig:methodology-keys}, where reads are plotted for each unique
state, or key, along the \(x\) axis. Keys are more popular than others (up to
\(5\times\)) because worker tasks start generating states with different
coordinates later in the run.  Figure~\ref{fig:methodology-keys} shows that the
number of reads changes with different initial conditions (\(\Delta\)), but
that the spatial locality of key accesses is similar ({\it e.g.}, some keys are
still \(5\times\) more popular than others).

Figure~\ref{fig:motivation-regimes} shows how entropy for different growth
rates has temporal locality, as the reads per second for \(\Delta_2\) look like
the reads per second for \(\Delta_1\) stretched out along the time axis.
Trends also exist for temperature and number of workers but are omitted here
for space. This structure means that we can learn the key access patterns and
adapt the storage system accordingly (this motivates
Section~\S\ref{sec:dom-specific}).

### 2017-11-28 paper/sections/4_dynamic-policies.tex
paper: more typos and final read through
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% technical details
The results for different cache sizes for a growth rate of \(\Delta_1\) over a
2.5 hour run across 256 workers is shown in
Figure~\ref{fig:methodology-tradeoff}.  ``Baseline" is the performance of
unmodified ParSplice  measured in trajectory duration (\(y1\) axis) and
utilization is measured with memory footprint of just the cache (\(y2\) axis).
The middle graph labeled ``Fixed Cache Size" shares the \(y\) axes and shows the
trade-off of using a basic LRU-style cache of different sizes, where the
penalty for a cache miss is retrieving the data from the persistent database.
We evict keys (if necessary) at every operation instead of when segments
complete because the cache fills up too quickly otherwise. This is implemented
using a ``when" policy of:

@@

The error bars are the standard deviation of 3 runs.  Although the keyspace
grows to 150K, a 100K key cache achieves 99\% of the performance. Decreasing
the cache degrades performance and predictability.

@@

% why is the performance lower for smaller caches?
But the top graph in Figure~\ref{fig:motivation-regimes} suggests that a
smaller cache size should suffice, as only 100 keys seem to be active at any
one time.  It turns out that the unique keys plotted in
Figure~\ref{fig:motivation-regimes} are per second and are not representative
of the actual active keyspace; the number of active keys is larger than 100, as
some keys may be accessed at time \(t_0\), not in \(t_1\), and then again in
\(t_2\). Because the cache is too small, reads and writes hit rest of the
storage hierarchy and the excessive traffic triggers a LevelDB compaction on
the persistent database.  To avoid overloading the storage hierarchy with
requests, we design a multi-part policy that switches between:

@@

% results: same level of performance can be achieved 
The key observation is that small caches incur too much load on the persistent
database at the beginning of the run but should suffice after the initial read
flash crowd passes because the keyspace is far less active.  We program Mantle
to trigger the policy switch at 100K keys to absorb the flash crowd at the
beginning of the run. Once triggered, keys are evicted to bring the size of the
cache down to the threshold.  The actual policy is shown and described in more
detail in the next section in Figure~\ref{src:lru-dyn}.  The plot on the right
side of Figure~\ref{fig:methodology-tradeoff} shows the performance/utilization
trade-off of the multi-part policy, where the cache sizes for the \(n\) key
limit policy are along the \(x\) axis.  The performance and memory utilization
for a 100K key cache size is the same as the 100K bar in the ``Fixed Cache
Size" graph in Figure~\ref{fig:methodology-tradeoff} but the rest reduce the
size of the keyspace after the read flash crowd.  We see the worst performance
when the engine switches to the 10 key limit policy, which achieves 94\% of the
performance while only using 40KB of memory.

@@

if #fans < 2 then -- do not evict current fan
  return false 
else
  WRstate(fans[#fans-1]['top']-fans[1]['bot'])
  return true
end
\end{minted}
\caption{The dynamically sized cache policy, whose performance is shown in 
Figure~\ref{fig:cache-management}, iterates backwards over timestamp-key pairs
and detects when key accesses move on to a new subset of
keys ({\it i.e.} ``fans"). \label{src:dyn-cache}}
\end{figure}

@@

Detecting these superbasins can lead to more effective cache management
strategies because the height of the groups of key accesses is ``how much" of
the cache to evict and the width of the groups of key accesses is ``when" to
evict values from the cache.  The zoomed portion of
Figure~\ref{fig:keyspace-zoomed} shows how a single superbasin affects the key
accesses. Moving along the \(x\) axis shows that the number of unique keys
accessed over time grows while moving along the \(y\) axis shows that early
keys are accessed more often.  Despite these patterns, the following
characteristics of superbasins make it hard to detect them:

@@

After trying these techniques we found that the basic algorithm in
Figure~\ref{src:dyn-cache} works best. The algorithm detects groups of key
accesses, which we call ``fans", by iterating backwards through the key access
trace, finding the lowest key ID, and comparing against the lowest key ID we
have seen so far (Line 7). We also maintain the top and bottom of each group of
key accesses (Line 13) so we can tell the ``how much" policy the number of keys
to evict (Line 19).  The algorithm is O(\(n\)), where \(n\) is the number
events, but the benefit is that the approach avoids adding new thresholds for
key access pattern detection ({\it e.g.}, space between key accesses, space
between key IDs, and window size of consecutive key accesses).

>>>>

% technical details
We implement a basic LRU cache using a ``when" policy of:

@@

The results for different cache sizes for a growth rate of \(\Delta_1\) over a
2.5 hour run across 256 workers is shown in
Figure~\ref{fig:methodology-tradeoff}.  ``Baseline" is the performance of
unmodified ParSplice  measured in trajectory duration (\(y1\) axis) and
utilization is measured with memory footprint of just the cache (\(y2\) axis).
The middle graph labeled ``Fixed Cache Size" shares the \(y\) axes and shows
the trade-off of using a basic LRU-style cache of different sizes, where the
penalty for a cache miss is retrieving the data from the persistent database.
The error bars are the standard deviation of 3 runs.  Although the keyspace
grows to 150K, a 100K key cache achieves 99\% of the performance. Decreasing
the cache degrades performance and predictability.

@@

% why is the performance lower for smaller caches?
But the top graph in Figure~\ref{fig:motivation-regimes} suggests that a
smaller cache size should suffice, as only 100 keys seem to be active at any
one time.  It turns out that the unique keys plotted in
Figure~\ref{fig:motivation-regimes} are per second and are not representative
of the actual active keyspace; the number of active keys is larger than 100, as
some keys may be accessed at time \(t_0\), not in \(t_1\), and then again in
\(t_2\). Because the cache is too small, reads and writes fall through to the
rest of the storage hierarchy and the excessive traffic triggers a LevelDB
compaction on the persistent database.  To avoid these compactions, which
temporarily block operations, we design a multi-policy cache that switches
between:

@@

% results: same level of performance can be achieved 
The key observation is that small caches incur too much load on the persistent
database at the beginning of the run but should suffice after the initial read
flash crowd passes because the keyspace is far less active.  We program Mantle
to trigger the policy switch at 100K keys to absorb the flash crowd at the
beginning of the run. Once triggered, keys are evicted to bring the size of the
cache down to the threshold.  The actual policy is shown and described in more
detail in Section~\S\ref{sec:scope} in Figure~\ref{src:lru-dyn}.  The plot on
the right side of Figure~\ref{fig:methodology-tradeoff} shows the
performance/utilization trade-off of the multi-policy cache, where the cache
sizes for the \(n\) key limit policy are along the \(x\) axis.  The performance
and memory utilization for a 100K key cache size is the same as the 100K bar in
the ``Fixed Cache Size" graph in Figure~\ref{fig:methodology-tradeoff} but the
rest reduce the size of the keyspace after the read flash crowd.  We see the
worst performance when the policy switches to the 10 key limit policy, which
achieves 94\% of the performance while only using 40KB of memory.

@@

if #fans < 2 then -- do not evict current fan
  return false
else
  WRstate(fans[#fans-1]['top']-fans[1]['bot']) 
  return true
end
\end{minted}
\caption{The dynamically sized cache policy iterates backwards over
timestamp-key pairs and detects when accesses move on to a new subset of keys
({\it i.e.} ``fans"). The performance and total memory usage is in
Figure~\ref{fig:dscache-vs-none} and the memory usage over time is in
Figure~\ref{fig:memory-vs-time}.
\label{src:dyn-cache}}
\end{figure}

@@

Detecting these superbasins can lead to more effective cache management
strategies because the height of the groups of key accesses is ``how much" of
the cache to evict and the width of the groups of key accesses is ``when" to
evict values from the cache.  The zoomed portion of
Figure~\ref{fig:keyspace-zoomed} shows how a single superbasin affects the key
accesses. Moving along the \(x\) axis shows that the number of unique keys
accessed over time grows while moving along the \(y\) axis shows that early
keys are accessed more often.  Despite these patterns, the following
characteristics of superbasins make them hard to detect:

@@

After trying these techniques we found that the basic O(\(n\)) algorithm in
Figure~\ref{src:dyn-cache} works best. The algorithm detects groups of key
accesses, which we call ``fans", by iterating backwards through the key access
trace, finding the lowest key ID, and comparing against the lowest key ID we
have seen so far (Line 7). We also maintain the top and bottom of each group of
key accesses (Line 13) so we can tell the ``how much" policy the number of keys
to evict (Line 23).  The algorithm is O(\(n\)), where \(n\) is the number
events, but the benefit is that the approach avoids adding new thresholds for
key access pattern detection ({\it e.g.}, space between key accesses, space
between key IDs, and window size of consecutive key accesses).

### 2017-11-28 paper/sections/5_file-systems.tex
paper: more typos and final read through
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \footnotesize
        \centering
        \begin{minted}[xleftmargin=3em,linenos]{lua}
function when()
  if server[whoami]['cachesize'] > n then
    if server[whoami]['cachesize'] > 100K then
      WRstate(1)
    end
    if RDstate() == 1 then
      return true
    end
  end
  return false
end
        \end{minted}
        \caption{ParSplice cache management policy that absorbs the burstiness of the
        workload before switching to a constrained cache.  The
        performance/utilization for different  \texttt{n} is in
        Figure~\ref{fig:methodology-tradeoff}. \label{src:lru-dyn}}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \footnotesize
        \begin{minted}[xleftmargin=3em,linenos]{lua}
local function when()
  if servers[whoami]["load"] > target then
    overloaded = RDstate() + 1
    WRstate(overloaded)
    if overloaded > 2 then
      return true
    end
  end
  else then WRstate(0) end
  return false
end
        \end{minted}
	\caption{CephFS file system metadata load balancer, designed in 2004
        in~\cite{weil:sc2004-dyn-metadata}, reimplemented in Lua
        in~\cite{sevilla:sc15-mantle}. This policy has many similarities to the
        ParSplice cache management policy.\label{src:lua-cephfs}}
    \end{subfigure}
    \caption{ParSplice's cache management policy has the same components as
    CephFS's load balancing policy.}
\end{figure*}

%\begin{itemize}
%  \item Lustre Trace
%  \item LinkedIn Trace
%  \item Nathan's Trace
%\end{itemize}

@@

These similarities among effective policies for two very different domains
suggest that the heuristics and techniques in other load balancers can be used
for cache management. The result support the notion that concepts and problems
that architects grapple with are transcendent and the solutions they design can
be re-used in different code bases.

@@

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/trace-atime.png}\\
\caption{File system metadata reads for a Lustre trace collected at LANL. The
vertical lines are the access patterns detected by the ParSplice cache
management policy from Section~\S\ref{sec:dom-specific}. The policy works
``out-of-the-box", which suggests that data management policies are general and
can be used across domains.
\label{fig:trace-atime}}
\end{figure}

@@

% other use cases caches/tiers 
Storage systems have many other data management techniques that would benefit
from the caching policies developed in Sections~\S\ref{sec:arch-specific}
and~\ref{sec:dom-specific}. For example, Ceph administrators can use the
policies in ParSplice to automatically size and manage cache
tiers\footnote{http://docs.ceph.com/docs/master/rados/operations/cache-tiering/},
caching on object storage devices, or in the distributed block
devices\footnote{http://docs.ceph.com/docs/master/rbd/rbd-config-ref/}.
Integration with Mantle would be straightforward as it is merged into Ceph's
mainline\footnote{http://docs.ceph.com/docs/master/cephfs/mantle/} and the
three caching subsystems mentioned above already maintain key access traces.

>>>>

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \footnotesize
        \centering
        \begin{minted}[xleftmargin=3em,linenos]{lua}
function when()
  if server[whoami]['cachesize'] > n then
    if server[whoami]['cachesize'] > 100K then
      WRstate(1)
    end
    if RDstate() == 1 then
      return true
    end
  end
  return false
end
        \end{minted}
        \caption{ParSplice cache management policy that absorbs the burstiness of the
        workload before switching to a constrained cache.  The
        performance/utilization for different  \(n\) is in
        Figure~\ref{fig:methodology-tradeoff}. \label{src:lru-dyn}}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \footnotesize
        \begin{minted}[xleftmargin=3em,linenos]{lua}
local function when()
  if servers[whoami]["load"] > target then
    overloaded = RDstate() + 1
    WRstate(overloaded)
    if overloaded > 2 then
      return true
    end
  end
  else then WRstate(0) end
  return false
end
        \end{minted}
	\caption{CephFS file system metadata load balancer, designed in 2004
        in~\cite{weil:sc2004-dyn-metadata}, reimplemented in Lua
        in~\cite{sevilla:sc15-mantle}. This policy has many similarities to the
        ParSplice cache management policy.\label{src:lua-cephfs}}
    \end{subfigure}
    \caption{ParSplice's cache management policy has the same components as
    CephFS's load balancing policy.}
\end{figure*}

@@

These similarities among effective policies for two very different domains
suggest that the heuristics and techniques in other load balancers can be used
for cache management. The result supports the notion that concepts and problems
that architects grapple with are transcendent across domains and the solutions
they design can be re-used in different code bases.

@@

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/trace-atime.png}\\
\caption{File system metadata reads for a Lustre trace collected at LANL. The
vertical lines are the access patterns detected by the ParSplice cache
management policy from Section~\S\ref{sec:dom-specific}. A file system that
load balances metadata across a cluster of servers could use the same pattern
detection to make migration decisions, such as avoiding migration when the
workload is accessing the same subset of keys or keeping groups of accesses
local to a server.  \label{fig:trace-atime}}
\end{figure}

@@

% other use cases caches/tiers 
Storage systems have many other data management techniques that would benefit
from the caching policies developed in Sections~\S\ref{sec:arch-specific}
and~\S\ref{sec:dom-specific}. For example, Ceph administrators can use the
policies in ParSplice to automatically size and manage cache
tiers\footnote{http://docs.ceph.com/docs/master/rados/operations/cache-tiering/},
caching on object storage devices, or in the distributed block
devices\footnote{http://docs.ceph.com/docs/master/rbd/rbd-config-ref/}.
Integration with Mantle would be straightforward as it is merged into Ceph's
mainline\footnote{http://docs.ceph.com/docs/master/cephfs/mantle/} and the
three caching subsystems mentioned above already maintain key access traces.
